### 2014-03-15 src/discussion.Rnw
Fix high/low

Our \textit{round(x)}, the strategy of ignoring low complexity elements,
did not pay off, with line scope having a tendency to become unstable and
inaccurate at high sampling ratios. At very low sampling ratio ($1/64$), the
strategy with method scope also becomes unstable and inaccurate. On the whole
\textit{round(x)} did not perform as well as \textit{sample(x)}

>>>>

Our \textit{round(x)}, the strategy of ignoring low complexity elements,
did not pay off, with line scope having a tendency to become unstable and
inaccurate at low sampling ratios. At very low sampling ratio ($1/64$), the
strategy with method scope also becomes unstable and inaccurate. On the whole
\textit{round(x)} did not perform as well as \textit{sample(x)}
